Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-17 paper-2023-acsos-pulverization.tex
write a section on limitations

\subsection{Limitations}

@@

>>>>

The configuration produced by the \ac{dsl} needs a platform that instructs the system on the way actual communication needs to be performed.
%
In our current implementation,
we provide out of the box a JVM platform based on the MQTT protocol
and supporting both intra- and inter-device communication.
%
For the large scale experiment,
we implemented a second platform,
this time to comply with the requirements of the simulation engine we used.
%
The implementation required little effort,
and it has been made available as part of the evaluation repositories.

\subsection{Limitations of the current version of the DSL}

In its current form, the proposed \ac{dsl} has two major limitations.
%
First and foremost, currently it does not consider openness:
hosts get specified in the runtime and reconfiguration \ac{dsl} as a closed set,
so the specification is not robust to the addition of new hosts or the loss of existing ones.
%
This is a major limitation that,
although planned to be addressed shortly with minor additions to the \ac{dsl},
must be highlighted in this manuscript.
%
The second limitation is related to the policies that can be expressed in the reconfiguration \ac{dsl}:
currently, only policies that can be assessed at the local host level can be assessed.
%
A policy that requires to consider the state of multiple hosts would require to resort to the host language primitive mechanisms and make explicit communications outside the framework,
thus breaking the abstraction.
%
This limitation can be addressed by extending the current reconfiguration
block of the \ac{dsl} in such a way that queries can be performed on any reachable host of the system,
thus making all communications
(including reconfiguration-related ones)
pass through the channels controlled by the framework.

@@

more platforms
